Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-11 paper/paper.tex
Committing from -2ft

Let $p$ be a vertex in a graph $P$, the \emph{degree} of $p$, $\deg(p)$, is the number of vertices
to which it is adjacent

>>>>

Let $p$ be a vertex in a graph $P$. The \emph{degree} of $p$, $\deg(p)$, is the number of vertices
to which it is adjacent. The degree of vertices gives us an invariant, which may be used to
eliminate some infeasible values from domains.
